Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-02-25 analysis/paper.Rmd
suppressing gpa progress bar
-removed fill="none" in order to avoid kniti issues -adjustment of fig8.1

# GPA is performed on the lances, including the semi-landmarks at the socket.
lancespr<-gpagen(lances_geo)  # GPA of all lances

@@

upper_fn <- function(data, mapping, ...){
  p <- ggplot(data = data, mapping = mapping) + 
    geom_smooth(method=loess, fill="None", color="Black", ...) +
    geom_point(aes(color=site, alpha=0.5))
  p
}

@@

#Copied to try to adjust to get to knit in Thomas's env
#COMMENTED OUT BY THOMAS IN ORDER TO KNIT
pairs_fig <- ggpairs(lances_M, columns = c('total_length', 'blade_length', 'socket_length', 'sock_bdiam', 'sock_sdiam', 'width', 'thickness'),  
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() #+
        #ggsave(here("Images","replication_fig_8v1.png"))
print(pairs_fig, progress = F)

>>>>

# GPA is performed on the lances, including the semi-landmarks at the socket.
lancespr<-gpagen(lances_geo, print.progress = FALSE)  # GPA of all lances

@@

#upper_fn <- function(data, mapping, ...){
#  p <- ggplot(data = data, mapping = mapping) + 
#    geom_smooth(method=loess, fill="None", color="Black", ...) +
#    geom_point(aes(color=site, alpha=0.5))
#  p
#}

#REMOVED fill="None"
upper_fn <- function(data, mapping, ...){
  p <- ggplot(data = data, mapping = mapping) + 
    geom_smooth(method=loess, color="Black", ...) +
    geom_point(aes(color=site, alpha=0.5))
  p
}

@@

#Copied to try to adjust to get to knit in Thomas's env
#pairs_fig <- ggpairs(lances_M, columns = c('total_length', 'blade_length', 'socket_length', 'sock_bdiam', #'sock_sdiam', 'width', 'thickness'),  
#        upper=list(continuous = upper_fn),
#        diag=list(continuous = diag_fn),
#        lower=list(continuous = "cor")) + theme_minimal() #+
#        #ggsave(here("Images","replication_fig_8v1.png"))
#print(pairs_fig, progress = F)
